MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
calculate shooting distance vs accuracy

#set the value to numeric or integer accordingly
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[, "PTS_TYPE"] <- as.integer(df[, "PTS_TYPE"])
df[, "CLOSE_DEF_DIS"] <- as.numeric(df[, "CLOSE_DEF_DIST"])

@@

#combine point type and distance
valid_distance = data.frame(point_type, distance)

@@

@@

@@

I   What would be the next steps?
---

>>>>

#set the value to numeric or integer accordingly
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[, "PTS_TYPE"] <- as.integer(df[, "PTS_TYPE"])
df[, "CLOSE_DEF_DIST"] <- as.character(df[, "CLOSE_DEF_DIST"])

#Calculate accuracy against defender distance
#Group the defender distance level
distance_level <- as.data.frame(table(factor(ClosestDefenderDistance)))
head(distance_level)

#Calculate how many times players scored in every defender distance
for (i in 1:nrow(distance_level)){
  distance_level[i, "SCORED"] <- sum(df[df[, "CLOSE_DEF_DIST"] == distance_level[i, "Var1"], "FGM"])
}

#Calculate shooting accuracy for each distance
distance_level$Accuracy <- round(distance_level$SCORED / distance_level$Freq, 2)

#Plotting the result
library(ggplot2)
ggplot(data = distance_level, aes(x = distance_level$Var1, y = distance_level$Accuracy)) +
  geom_point(aes(x = distance_level$Var1, y = distance_level$Accuracy))

#Calculate accuracy against shooting distance
#Group the shooting distance level
shooting_distance_level <- as.data.frame(table(factor(ShotDistance)))
head(shooting_distance_level)

#Calculate how many times players scored in every shooting distance
for (i in 1:nrow(shooting_distance_level)){
  shooting_distance_level[i, "SCORED"] <- sum(df[df[, "SHOT_DIST"] == shooting_distance_level[i, "Var1"], "FGM"])
}

#Calculate shooting accuracy for each distance
shooting_distance_level$Accuracy <- round(shooting_distance_level$SCORED / shooting_distance_level$Freq, 2)

#Plotting the result
library(ggplot2)
ggplot(data = shooting_distance_level, aes(x = shooting_distance_level$Var1, y = shooting_distance_level$Accuracy)) +
  geom_point(aes(x = shooting_distance_level$Var1, y = shooting_distance_level$Accuracy))

@@

#combine point type and distance

valid_distance = data.frame(point_type, distance, shot_dist)
dist_group <- c(3, 6, 9, 12, 15, Inf)
valid_distance[, "Range_Group"] <- c(findInterval(valid_distance$distance, dist_group))

valid_distance = data.frame(point_type, distance)

@@

ggplot(data = valid_distance, aes(x = Range_Group)) + geom_bar()

ggplot(data = valid_distance, aes(x = distance) + geom_bar())

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Discussion
I   What results did you find?

@@

Justin Leiendecker, Alexander Romanenko, Artmeis Tomadaki-Balomenou, Zijun Wei, Reza Brianca Widodo
